Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Summer Wrap Up

### 2024-01-22 summer_2023/aug08meeting_pres4/may30ccgmeeting.tex
new presentation started

	\section{Takeaways \& Tips}
	\begin{frame}{Experience Gained (Technical Skills)}

	\begin{frame}{Experience Gained (Personal Skills)}
		content...
	\end{frame}

	\begin{frame}{Major Takeaways for Future Undergrads}
		\begin{itemize}
			\item 
		\end{itemize}
	\end{frame}

>>>>

	\section{Takeaways \& Tips}
	\begin{frame}{Experience Gained (Technical Skills)}
		\includegraphics[width=\textwidth,height=8cm]{technical_skills_gained.png}
	\end{frame}

	\begin{frame}{Experience Gained (Personal Skills)}
		\begin{figure}
			\includegraphics[width=\textwidth,height=8cm]{soft_skills_gained.png}
		\end{figure}
	\end{frame}

	\begin{frame}{Major Takeaways for Future Undergrads}
		\begin{enumerate}
			\item Documentation and Organization: Document daily tasks in a manner that is easy for you AND others to understand. This helps keep track of your progress and helps explain things you did to other individuals in a clear and concise way.
			\item Think like a scientist: You are surrounded by brilliant minds, pay attention to how they come up with a solution when you go to them with a problem. Be creative and try to develop your own solutions, new ideas are always welcome.
			\item Be Confident: Speak up, ask questions, get involved. You are here to learn, nobody will shame you for that. Sometimes things can go much faster when you just ask.
		\end{enumerate}
	\end{frame}
